---
title: "PS4"
author: "Lan Shi 60625430"
date: "12/11/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r ps4_q1_source,echo=FALSE, message = FALSE}
source('ps4_q1.R')
knitr::kable(t1, align = 'r', caption="All-time Leader in Hits for Each Birth Country")
```

## Question 2
#### a)
```{r ps4_q2a_source, echo=FALSE,message = FALSE}
source('ps4_q2a.R')
knitr::kable(result_a, align = 'r', caption="Results for q2 (a)")
```

#### b) c) Results are in the corresponding files.
Since I didn't get my flux account in time, Prof. Henderson excused me from the flux portions of the assignment and asked me to do something else. Here is the requirement:   
"You should still do Q2 parts b and c but:    

 for 2b, you can simply run your script on mario or luigi (scs.dsc.umich.edu)  
 for 2c, you should still right a script that runs in batch mode but you don't need to use a job array to run it.   

 Instead of using a job array for 2c, run your script as Rscript ps4_q2c.R sigma mc_rep n_cores (manually) for each of the different values of sigma."  
  
##### Thus, the files I submitted are: ps4_q2_funcs.R, ps4_q2a.R, ps4_q2b.R, ps4_q2c.R, ps4_q2b.Rout, results_q4b.RData, ps4_q2c-X.Rout (X = 1, 2, 4), and "cmd for Rout files.txt" (a txt file including my cmd lines).

## Question 3



